% !TEX encoding = UTF-8 Unicode

\begin{thebibliography}{x}
\addcontentsline{toc}{chapter}{\bibname}

\bibitem{itu_ict_fac_fig_2017}
International Telecommunication Union: \emph{ICT Facts and Figures 2017}. International Telecommunication Union, 2017.

\bibitem{nav_online_szla}
Nemzeti Adó- és Vámhivatal, \emph{Online Számla}, \texttt{https://onlineszamla.nav.gov.hu}, Internet, 2018.

\bibitem{statcounter_os_market_share}
StatCounter, \emph{Operating System Market Share Hungary: July 2017 - July 2018},  \texttt{http://gs.statcounter.com/os-market-share/all/hungary}, Internet, 2018.

\bibitem{ecma_334_c_sharp}
ECMA International: \emph{ECMA-334 C\# Language Specification, 5th Edition}, ECMA International, 2017.

\bibitem{iso_iec_c_sharp_2006}
International Organization for Standardization, \emph{ISO/IEC 23270:2006(E), Second Edition}, International Organization for Standardization, 2006.

\bibitem{iso_iec_dis_c_sharp_future}
International Organization for Standardization, \emph{ISO/IEC DIS 23270}, \texttt{https://www.iso.org/standard/75178.html}, Internet, 2018.

\bibitem{ecma_335_cli_dotnet}
ECMA International: \emph{Common Language Infrastructure (CLI), 6th Edition}, ECMA International, 2012.

\bibitem{iso_iec_cli_dotnet_2012}
International Organization for Standardization, \emph{ISO/IEC 23271:2012(E), Third Edition}, International Organization for Standardization, 2012.

\bibitem{kovacs_laszlo_adatbazisok}
Kovács László: \emph{Adatbázisok tervezésének és kezelésének módszertana}, ComputerBooks, Budapest, 2004.

\bibitem{iso_iec_sql}
International Organization for Standardization, \emph{ISO/IEC 9075:2016, Fifth Edition}, International Organization for Standardization, 2016.

\bibitem{whats_new_in_sql}
Modern SQL: \emph{What's New in SQL:2016}, \texttt{https://modern-sql.com/blog/2017-06/whats-new-in-sql-2016}, Internet, 2017.










\begin{comment}

%innentol a vecsie!
\bibitem{intellipaint}
Reese, L. Jack, and William A. Barrett. \emph{Image editing with intelligent paint}. Proceedings of Eurographics. Vol. 21. No. 3. 2002.

\bibitem{instagram}
Instagram, hivatalos weboldal, \texttt{https://www.instagram.com/}, Internet, 2018.

\bibitem{snapchat}
Snapchat, hivatalos weboldal, \texttt{https://www.snapchat.com/}, Internet, 2018.

\bibitem{messenger}
Facebook messenger, hivatalos weboldal, \texttt{https://www.messenger.com/features}, Internet, 2018.

\bibitem{prisma}
Prisma, hivatalos weboldal, \texttt{https://prisma-ai.com/}, Internet, 2018.

\bibitem{pixect}
Pixect, hivatalos weboldal, \texttt{https://www.pixect.com/}, Internet, 2018.

\bibitem{jetset}
Smilebit: \emph{Jet Set Radio}, SEGA, \texttt{http://www.sega.com/games/jet-set-radio}, Internet, 2003.

\bibitem{scannerdarkly}
The New York Times, \emph{'A Scanner Darkly': Keanu Reeves, Undercover and Flying High on a Paranoid Head Trip}, 2006. július 7.

\bibitem{porthu}
Port.hu, \emph{Kamera által homályosan}, \texttt{https://port.hu/adatlap/film/tv/kamera-altal-\\homalyosan-a-scanner-darkly/movie-82437}, Internet, 2006.

\bibitem{czap}
Czap László: Képfeldolgozás, egyetemi jegyzet, Miskolci Egyetem, \\ \texttt{http://mazsola.iit.uni-miskolc.hu/~czap/HEFOP/Kepfeld1010.pdf}, 2007.

\bibitem{kato}
Kató Zoltán: Digitális képfeldolgozás, egyetemi kurzus, Szegedi Tudományegyetem, \texttt{http://www.inf.u-szeged.hu/~kato/teaching/DigitalisKepfeldolgozasTG}, 2014.

\bibitem{bilateral}
Paris, Sylvain, et al. \emph{A gentle introduction to bilateral filtering and its applications}. ACM SIGGRAPH 2007 courses. ACM, 2007.

\bibitem{sobel}
Utkarsh Sinha: \emph{The Sobel and Laplacian Edge Detectors}, \texttt{http://aishack.in/tutorials/sobel-laplacian-edge-detectors/}, 2010.

\bibitem{beyeler} Michael Beyeler: \emph{How to create a cool cartoon effect with OpenCV and Python}, \texttt{http://www.askaswiss.com/2016/01/} \texttt{how-to-create-cartoon-effect-opencv-python.html}, 2016. január 5.

\bibitem{beyeler2} Michael Beyeler: \emph{How to create a beautiful pencil sketch effect with OpenCV and Python}, \texttt{http://www.askaswiss.com/2016/01/} \texttt{how-to-create-pencil-sketch-opencv-python.html}, 2016. január 13.

\bibitem{emami} Shervin Emami: \emph{Mastering OpenCV with Practical Computer Vision Projects}, Packt Publishing, 2012.

\bibitem{opencv}
Bradski, Gary, and Adrian Kaehler. Learning OpenCV: \emph{Computer vision with the OpenCV library}. O'Reilly Media, Inc., 2008.

% TODO: Artistic filter-es könyv.

\end{comment}

\end{thebibliography}